A survey of HTTP caching implementations on the open Semantic Web

### 2015-03-19 sanity/paper1.tex
Generic web servers
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1105 43ef1190-90fd-4dd7-a769-d0121f02b80e

For each unique \httph{Server} header, we found the ones where
\emph{all} responses had a freshness lifetime or other usable
metadata. For the former, this amounted to 22 servers, which are
listed in Table~\ref{tab:servers}.  70 servers always responded with
usable metadata. Inspecting the values we find the well-known Virtuoso
and Callimachus servers, as well as the Perl modules
RDF::LinkedData and RDF::Endpoint, which are partly
developed by and run on a server operated by this author. Apart from
those, we see that the they reveal very little about the RDF-specific
parts of the underlying server implementation. A quick inspection of
all \httph{Server} headers confirmed that few reveal any further
detail.

>>>>

For each unique \httph{Server} header, we found the ones where
\emph{all} responses had a freshness lifetime or other usable
metadata. For the former, this amounted to 22 servers, which are
listed in Table~\ref{tab:servers}.  70 servers always responded with
usable metadata. Inspecting the values we find the well-known Virtuoso
and Callimachus servers, as well as the Perl modules
RDF::LinkedData and RDF::Endpoint, which are partly
developed by and run on a server operated by this author. Apart from
those, we see that the they reveal very little about the RDF-specific
parts of the underlying server implementation, e.g. Apache
is a very common generic Web server, the others are also generic. A quick inspection of
all \httph{Server} headers confirmed that few reveal any further
detail.
